---
title: "Simulate and analyze data"
author: "Chris McKennan"
date: "2025-10-14"
output: html_document
---

# Load data and source functions
```{r LoadData}
tmp <- load("SimulationParams.RData")

source("SimulateData.R")
source("EstimateModelParams2.R")
source("Prediction2.R")
```

# Set parameters
Parameters chosen to match INSPIRE discovery data
```{r SetParameters}
min.dob <- as.Date("2012-06-01")
max.dob <- as.Date("2013-12-31")
n <- 1713
n.miss <- 579
```

# Simulate data
```{r SimulateData}
#Simulate birth dates#
DOB.sim <- as.Date("2012-06-01") + runif(n = floor(n/2), min = 0, max = as.numeric(as.Date("2012-12-31")-as.Date("2012-06-01")))
DOB.sim <- c(DOB.sim, as.Date("2013-06-01") + runif(n = n-length(DOB.sim), min = 0, max = as.numeric(as.Date("2013-12-31")-as.Date("2013-06-01"))))
DOB.sim <- sort(as.Date(DOB.sim))

#Generate Covariates#
Cov.sim <- Cov.sim[order(runif(n)),]

#Compute probabilities#
Prob.sim <- PredictCondDensity(Lambda = Lambda, DOB = DOB.sim, a.max = 365, knots = Knots, degree = 3, Alpha = W.params.true, Cov = Cov.sim, Beta = beta.true, Mu = rep(0,length(beta.true)), Month.use = 1:12, Cond.Prob = F)

#Simulate data#
Sim.Data <- SimulateData(DOB = DOB.sim, P.RSV = Prob.sim$Prob, n.miss = n.miss)
Sim.Data$Date.RSV <- Sim.Data$DOB + Sim.Data$Age.RSV
```

# Estimate parameters
```{r EstimateParameters}
#Create dataset#
Dataset.Sim <- Get.Data(degree = 3, n.internal.knots = 10, Lambda = Lambda, Date.RSV = Sim.Data$Date.RSV, RSV.status = Sim.Data$RSV.1year, DOB = Sim.Data$DOB, Cov = Cov.sim)
Dataset.True <- Get.Data(degree = 3, n.internal.knots = 10, Lambda = Lambda, Date.RSV = Sim.Data$Date.RSV, RSV.status = Sim.Data$RSV.1year, DOB = Sim.Data$DOB, Cov = Cov.sim, knots = Knots)  #Used to plot the ground-truth weight function.

#Estimate parameters#
Lambda.Kfold.Sim <- Choose.Lambda(Data = Dataset.Sim, n.folds = 10, n.lambda = 400, max.lambda=1e3)
Fit.Sim <- Optimize.W.Cov(Data = Dataset.Sim, lambda = nrow(Dataset.Sim$Cov)*Lambda.Kfold.Sim$lambda.opt, max.iter = 200); names(Fit.Sim$beta) <- c("White","Male","Daycare","OlderSiblings")
```

# Plot results
Solid black line: estimate\\
Dashed lines: 95% confidence intervals\\
Red line: simulated ground-truth weight function\\
Note: the dashed lines are point-wise confidence intervals, not confidence bands. Therefore, the red line is not expected to lie within the dashed lines at every point. 
```{r Plot}
alpha.plot <- 0.05
Se.fit.Sim <- Var.Pred.Cov(Alpha = Fit.Sim$Alpha, Beta = Fit.Sim$beta, Data = Dataset.Sim, lambda = nrow(Dataset.Sim$Cov)*Lambda.Kfold.Sim$lambda.opt, units = "months", plot.it = F)
Se.fit.Sim.True <- Var.Pred.Cov(Alpha = W.params.true, Beta = beta.true, Data = Dataset.True, lambda = nrow(Dataset.Sim$Cov)*Lambda.Kfold.Sim$lambda.opt, units = "months", plot.it = F)

plot(Se.fit.Sim$x.plot, Se.fit.Sim$W.hat, type = "l", lwd=2, xlab="", xlim=c(0,365/30), ylim=c(0,max(c(Se.fit.Sim$W.hat+qnorm(1-alpha.plot/2)*Se.fit.Sim$se.W.hat,Se.fit.Sim.True$W.hat))), ylab="", axes=F)
lines(Se.fit.Sim$x.plot, Se.fit.Sim$W.hat - qnorm(1-alpha.plot/2)*Se.fit.Sim$se.W.hat, lty=2); lines(Se.fit.Sim$x.plot, Se.fit.Sim$W.hat + qnorm(1-alpha.plot/2)*Se.fit.Sim$se.W.hat, lty=2)
axis(side = 1, at = seq(0,365/30,length=13), labels = 0:12); axis(side = 2, at = pretty(c(Se.fit.Sim$W.hat,Se.fit.Sim$W.hat - qnorm(1-alpha.plot/2)*Se.fit.Sim$se.W.hat,Se.fit.Sim$W.hat + qnorm(1-alpha.plot/2)*Se.fit.Sim$se.W.hat)))
title(xlab = expression(paste("Age ",italic(a)," (months)")), ylab = expression(paste("Weight function estimate ",hat(italic(w)),"(",italic(a),")")), line = 2.3)

lines(Se.fit.Sim.True$x.plot, Se.fit.Sim.True$W.hat, col="red")
```